Architectures and Open pNets

### 2018-02-08 2018-Arch-pNets/arch-pNets.tex
Added the architecture composition

\usepackage{amsmath,amsthm,amscd}
\usepackage{amssymb}  %for blackboard B
\usepackage{rotating} %to rotate the figures
\usepackage{mathpartir} % math paragraph + inference rules
\usepackage{caption}
\usepackage{xifthen}
\usepackage{stmaryrd} % double brackets (\llbracket, \rrbracket)

@@

\newcommand{\data}{\ensuremath{\sD}}
\newcommand{\guards}[1]{\ensuremath{\sB_{#1}}}
\newcommand{\exprs}[1]{\ensuremath{\sE_{#1}}}
\newcommand{\valuations}[1]{\ensuremath{\sV_{#1}}}
\newcommand{\val}[3][]{%
  \ensuremath{\sigma^{#2}_{#3}%
    \ifthenelse{\isempty{#1}}{}{(#1)}%
  }%
}
%% \DeclareMathOperator{\supp}{supp}
\newcommand{\supp}[1]{\ensuremath{\mathrm{supp}(#1)}}
\newcommand{\semopen}[1]{\ensuremath{[{#1}]}}
\newcommand{\semclosed}[1]{\ensuremath{\llbracket{#1}\rrbracket}}
\newcommand{\reachable}[1]{\ensuremath{\mathit{reachable}({#1})}}
\newcommand{\IMextend}[2]{\ensuremath{#1 \ltimes #2}}

@@

\begin{definition}[Composition of architectures]
  \label{defn:arch:composition}

\end{definition}

>>>>

\usepackage{amsmath,amsthm,amscd}
\usepackage{amssymb}    % for blackboard B
\usepackage{rotating}   % to rotate the figures
\usepackage{mathpartir} % math paragraph + inference rules
\usepackage{mathtools}  % for align, multline etc.
\usepackage{caption}
\usepackage{xifthen}
\usepackage{stmaryrd} % double brackets (\llbracket, \rrbracket)

@@

\newcommand{\data}{\ensuremath{\sD}}
\newcommand{\guards}[1]{\ensuremath{\sB_{#1}}}
\newcommand{\exprs}[1]{\ensuremath{\sE_{#1}}}
\newcommand{\valuations}[1]{\ensuremath{\sV_{#1}}}
\newcommand{\val}[3][]{%
  \ensuremath{\sigma^{#2}_{#3}%
    \ifthenelse{\isempty{#1}}{}{(#1)}%
  }%
}
%% \DeclareMathOperator{\supp}{supp}
\newcommand{\supp}[1]{\ensuremath{\mathrm{supp}(#1)}}
\newcommand{\semopen}[1]{\ensuremath{[{#1}]}}
\newcommand{\semclosed}[1]{\ensuremath{\llbracket{#1}\rrbracket}}
\newcommand{\reachable}[1]{\ensuremath{\mathit{reachable}({#1})}}
\newcommand{\IMextend}[2]{\ensuremath{#1 \ltimes #2}}
\newcommand{\arcomp}{\oplus}
\newcommand{\Arcomp}{\Bigoplus}
\newcommand{\expmix}{\oplus}

@@

\begin{definition}[Composition of architectures]
  \label{defn:arch:composition}
  Let $A_i = (\cC_i, P_{A_i}, V_{A_i}, \Gamma_i)$, for $i = 1,2$,
  be two architectures.  The \emph{composition} of $A_1$ and
  $A_2$ is the architecture $A_1 \arcomp A_2 = (\cC_1 \cup \cC_2,
  P_{A_1} \cup P_{A_2}, V_{A_1} \cup V_{A_2}, \Gamma)$, where
%
  \begin{equation}
    \label{eq:arch:composition}
    \Gamma = \setdefb{
      (a, g_1 \land g_2, e_1 \expmix e_2) 
    }{
      (a \cap P_{A_i}, g_i, e_i) \in \Gamma_i,
      \text{ for } i = 1,2
    }
    \,.
  \end{equation}
\end{definition}

\begin{proposition}[Properties of $\arcomp$]
  \label{prop:arcomp:nice}
  Architecture composition $\arcomp$ is commutative and
  associative; it is idempotent if all coordinating components
  are deterministic; $A_{id} = \bigl(\emptyset, \emptyset,
  \emptyset, \{\emptyset\}\bigr)$ is its neutral element, \ie for
  any architecture $A$, we have $A \oplus A_{id} = A$.
  Furthermore, for any component $B$, we have $A_{id}(B) = B$.
  %PCA: replaced ``holds'' by ``we have''
\end{proposition}
%
\begin{proof}[Sketch of the proof]
  Commutativity and associativity follow from the corresponding
  properties of set union, Boolean conjunction and
  \todoSB{Check ``semi''}\hl{semilattice meet}.
%
  Suppose we have two architectures $A = A'$.  This does not
  necessarily mean that their sets of coordinating components
  coincide.  However, if all the involved coordinating components
  are deterministic, then, in any state of $(A \arcomp A')(\cB)$,
  both architectures will impose the same restrictions, enabling
  the same interactions between the coordinating and operand
  components.  Hence, we have $(A \arcomp A')(\cB) = A(\cB) =
  A'(\cB)$.  Since this holds for any set of components $\cB$, we
  conclude that $A \arcomp A' = A = A'$.
%
  The properties of $A_{id}$ follow immediately from the
  definitions of architecture application and composition.
\end{proof}

%****************************************************************
\subsection{Preservation of safety properties}
\label{secn:safety}
